Pillar 1 - Sequential Pattern Mining

### 2019-01-18 Pillar 1 - Sequential Pattern Mining.Rmd
statistics -student, course, concentration, cluster

library(tidyverse)
library(arules)
library(arulesSequences)
```

@@

student_statistics <- exploration %>%
  group_by(`Student ID Number`) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = mean(Grade), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5))

course_statistics <- exploration %>%
  group_by(`Course Code`) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = mean(Grade), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5)) %>%
  inner_join(d_course, by= c("Course Code" = "Code")) #to get only UCM courses for which we have statistics

#We have NA in grades. Something weird is happening. 
summary(str_detect(d_transcript$Grade, pattern="NA")) #shows NA's = 312 FALSE= 89069 WHY ARE THERE NAs?

has_na <- d_transcript %>%
  mutate(What = str_detect(Grade, pattern="NA")) %>%
  filter(is.na(What))
```
We have found some NA values for the grades! Students:
0177849- COR1003 & EMTH0001  +++++++++++++++ Master thesis should not be showing up! +++++++++++++
0177857
0222100
0270148
0313173
0317101
0317349

>>>>

library(tidyverse)
library(arules)
library(arulesSequences)

library(rlang)
```

@@

student_statistics <- exploration %>%
  group_by(`Student ID`) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = mean(Grade), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5))

course_statistics <- exploration %>%
  group_by(`Course ID`) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = round(mean(Grade), 2), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5)) %>%
  right_join(d_course, by = "Course ID")

concentration_statistics <- exploration %>%
  inner_join(select(d_course,-Period, -`Period (additional)`,-`Period (additional bis)`,-`Course Title`), by = "Course ID") %>%
  #left_join(select(d_course, `Course ID`, Concentration, `Concentration (additional)`), by = "Course ID") %>%
  gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
  group_by(Concentration) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = round(mean(Grade), 2), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5))

cluster_statistics <- exploration %>%
  inner_join(d_course, by = "Course ID") %>%
  group_by(Cluster) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = round(mean(Grade), 2), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5))
```
We have found some NA values for the grades! Students:

0177849 - COR1003 & EMTH0001  +++++++++++++++ Master thesis should not be showing up! +++++++++++++
0177857
0222100
0270148
0313173
0317101
0317349

```{r}
#We have NA in grades. Something weird is happening. 
summary(str_detect(d_transcript$Grade, pattern="NA")) #shows NA's = 312 FALSE= 89069 WHY ARE THERE NAs?

has_na <- d_transcript %>%
  mutate(What = str_detect(Grade, pattern="NA")) %>%
  filter(is.na(What))
```
